The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
rm johnson numbers

<!-- TODO: point to figure 1 -->
Habitat selection depends on the scale at which it is measured and a singular
scale is insufficient for generalizing across scales [@Mayor_2009]. Habitat
selection is measured using resource selection functions (RSFs), based on the
proportion of used and available resources for an animal [@Manly_1993;
@Boyce_1999]. Johnson (1980) identified four orders of habitat selection: (1)
the geographical range of a species, (2) the home range of an individual, (3)
the habitat patches within the home range and (4) specific resources within a
habitat patch. Moving past this hierarchical perspective, Mayor (2009) reviewed
types of scale relevant in measurement of habitat selection and recommend using
a continuum of scales for identifying characteristic scales of selection. For
example, @Mayor_2007 showed caribou select for shallow snow at all scales
and by using a continuum of scales, avoided the bias of predefined scales assumed to be associated with certain behaviors.

>>>>

<!-- TODO: point to figure 1 -->
Habitat selection depends on the scale at which it is measured and a singular
scale is insufficient for generalizing across scales [@Mayor_2009]. Habitat
selection is measured using resource selection functions (RSFs), based on the
proportion of used and available resources for an animal [@Manly_1993;
@Boyce_1999]. Johnson (1980) identified four orders of habitat selection:
the geographical range of a species, the home range of an individual, the habitat patches within the home range and specific resources within a
habitat patch. 
Moving past this hierarchical perspective, Mayor (2009) reviewed
types of scale relevant in measurement of habitat selection and recommend using
a continuum of scales for identifying characteristic scales of selection. 
<!-- highlight this -->A continuum of scales allows xyz advantage

For
example, @Mayor_2007 showed caribou select for shallow snow at all scales and <!--what else higlight-->
and by using a continuum of scales, avoided the bias of predefined scales assumed to be associated with certain behaviors.
